\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{url}
\usepackage{calc}
\usepackage{tikz}
\usetikzlibrary{positioning, arrows.meta, calc, shapes.geometric, fit, backgrounds}
\usepackage{multirow}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

%% ─── convenience macros ───────────────────────────────────────────────────────
\newcommand{\R}{\mathbb{R}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\G}{\mathcal{G}}
\newcommand{\Lc}{\mathcal{L}_c}
\newcommand{\Ls}{\mathcal{L}_s}
\newcommand{\Ltv}{\mathcal{L}_{tv}}

\begin{document}

%% ─── Title ────────────────────────────────────────────────────────────────────
\title{Neural Texture Stylization with Tactile Fidelity:\\
A Unified Diffusion and Style Transfer Pipeline\\
for 3D Surface Fabrication}

%% ─── Author ───────────────────────────────────────────────────────────────────
\author{
\IEEEauthorblockN{Omprakash Pugazhendhi}
\IEEEauthorblockA{
  \textit{Department of Computer Science and Engineering}\\
  \textit{Vellore Institute of Technology}\\
  Chennai, India\\
  omprakash.2021@vitstudent.ac.in
}
}

\maketitle

%% ─── Abstract ─────────────────────────────────────────────────────────────────
\begin{abstract}
Existing 3D model stylization systems optimize for visual fidelity alone: they
transfer the color and appearance of a reference material image onto a mesh
surface, but leave the geometry entirely unmodified. A wood-grain texture
applied to a 3D-printed object may render convincingly on screen yet feel
completely smooth in the hand because no surface microrelief is encoded.
We introduce a unified machine learning pipeline that addresses both the visual
and tactile dimensions of texture simultaneously. The system integrates three
complementary technologies: (i)~a ResNet-50 texture classifier fine-tuned on
the 47-class Describable Textures Dataset (DTD), used for category-aware
data curation; (ii)~three neural style transfer methods (VGG-19 Gram-matrix
optimization, Johnson fast residual networks, and Adaptive Instance
Normalization), which produce visually stylized reference images; and
(iii)~a Stable Diffusion 1.5 image-to-image model fine-tuned with Low-Rank
Adaptation (LoRA) to generate grayscale displacement heightfields from
single texture images. Generated heightfields are applied as per-vertex
displacements to arbitrary triangulated meshes via UV parameterization
computed by xatlas, and the result is exported as a standards-compliant GLB
file. We further support three-mode texture interpolation in pixel, AdaIN
feature, and CLIP embedding spaces, and provide a bridge to the
3DShape2VecSet vector-set 3D shape diffusion model for end-to-end
image-conditioned shape generation with applied tactile surface texture.
Quantitative evaluation on 500 DTD test images yields SSIM~0.387,
LPIPS~0.334, and FID~51.2 for the diffusion method, representing improvements
of 24\%, 21\%, and 25\% respectively over a gradient-based synthetic baseline.
An interactive Gradio web demonstration allows any user to upload a single
reference image and download a textured GLB model in under one minute on
consumer hardware without requiring model training.
\end{abstract}

\begin{IEEEkeywords}
texture synthesis, neural style transfer, diffusion models, heightfield
generation, digital fabrication, 3D surface stylization, LoRA fine-tuning,
tactile rendering, UV parameterization, CLIP embeddings
\end{IEEEkeywords}

%% ─── Introduction ─────────────────────────────────────────────────────────────
\section{Introduction}

The widespread availability of desktop 3D printers and cloud-based fabrication
services has democratized the production of custom physical objects. However,
control over surface texture — the microgeometry that determines both the visual
appearance and the tactile feel of a surface — remains a fundamental challenge.
Existing workflows fall into two categories: (a)~UV-mapped color textures that
affect appearance in renders but contribute no geometric relief, and
(b)~bump/normal maps that simulate shading variation in renderers but again
produce no physical geometry on the printed object. Neither approach produces
surfaces that feel like the reference material when touched.

A displacement map, or \emph{heightfield}, encodes the signed elevation of
each surface point relative to a base mesh. When a heightfield is baked into
the mesh geometry — by displacing vertices along their normals proportionally
to the heightfield value — the resulting object carries true surface relief
that both looks and feels like the target texture. The core research question
this paper addresses is: \emph{given only a single reference photograph of a
texture material, can we automatically generate a plausible heightfield that
captures the micro-relief structure of that material?}

Prior work has approached this from the fabrication side. TactStyle
\cite{b1} demonstrated that a fine-tuned diffusion model can generate
heightfields that fool human participants in psychophysical comparisons with
laser-scan ground truth. However, TactStyle ships as a Blender plugin with
no open-source training code, no neural style transfer baselines, no texture
interpolation capability, and no evaluation framework. Our work fills these
gaps and contributes a substantially richer open research artifact.

The main contributions of this paper are:
\begin{itemize}
  \item A \textbf{unified five-stage pipeline} connecting texture classification,
        neural style transfer, heightfield generation, 3D mesh displacement,
        and quantitative evaluation in a single open-source repository.
  \item \textbf{Three NST methods} (Gatys, Johnson, AdaIN) benchmarked against
        each other on DTD with SSIM and LPIPS metrics, providing a practical
        comparison for texture-specific style transfer.
  \item A \textbf{LoRA-fine-tuned Stable Diffusion heightmap generator} trained
        on synthetically generated paired data from DTD, with full training
        code and hyperparameter documentation.
  \item \textbf{Three-mode texture interpolation} in pixel, AdaIN feature, and
        CLIP embedding spaces, enabling continuous blending between two
        reference materials.
  \item A \textbf{bridge to 3DShape2VecSet} \cite{b12} for image-conditioned
        3D shape generation with automatic tactile texturing.
  \item A \textbf{Gradio interactive demonstration} and six documented Jupyter
        notebooks covering every stage of the pipeline.
\end{itemize}

The remainder of this paper is organized as follows. Section~II covers
mathematical preliminaries. Section~III reviews related work. Section~IV
describes the system architecture in detail. Section~V documents the dataset
and data preparation. Section~VI gives implementation details. Section~VII
presents experiments and ablations. Section~VIII describes the demo.
Section~IX discusses limitations and future directions.

%% ─── Preliminaries ────────────────────────────────────────────────────────────
\section{Mathematical Preliminaries}

\subsection{Denoising Diffusion Models}

A denoising diffusion probabilistic model (DDPM) \cite{b17} defines a forward
process that gradually corrupts a clean data point $\mathbf{x}_0 \sim
q(\mathbf{x}_0)$ with Gaussian noise over $T$ timesteps:
\begin{equation}
  q(\mathbf{x}_t \mid \mathbf{x}_0) =
    \mathcal{N}\!\left(\mathbf{x}_t;\,\sqrt{\bar\alpha_t}\,\mathbf{x}_0,\,
    (1-\bar\alpha_t)\mathbf{I}\right),
  \label{eq:ddpm_forward}
\end{equation}
where $\bar\alpha_t = \prod_{s=1}^{t}(1-\beta_s)$ and $\beta_s$ is a
noise schedule. A neural network $\epsilon_\theta(\mathbf{x}_t, t)$ is
trained to predict the added noise via the simplified objective
\begin{equation}
  \mathcal{L}_{\text{DDPM}} =
    \mathbb{E}_{\mathbf{x}_0,\epsilon,t}\!\left[
      \norm{\epsilon - \epsilon_\theta(\mathbf{x}_t,\,t)}_2^2
    \right].
  \label{eq:ddpm_loss}
\end{equation}
Latent diffusion models (LDM) \cite{b7} apply this process in a compressed
latent space $\mathbf{z} = \mathcal{E}(\mathbf{x})$ produced by a pre-trained
VAE encoder $\mathcal{E}$, substantially reducing computational cost while
preserving perceptual quality.

\subsection{Low-Rank Adaptation}

Full fine-tuning of an LDM requires updating all parameters $\Theta$ of the
UNet backbone ($\approx$860\,M for SD\,1.5), which is memory-prohibitive for
single-GPU setups. LoRA \cite{b8} constrains weight updates to a
low-rank factorization: for a pre-trained weight matrix $\mathbf{W}_0 \in
\R^{d \times k}$, the adapted weight is
\begin{equation}
  \mathbf{W} = \mathbf{W}_0 + \Delta\mathbf{W},\quad
  \Delta\mathbf{W} = \frac{\alpha}{r}\,\mathbf{B}\mathbf{A},
  \label{eq:lora}
\end{equation}
where $\mathbf{A} \in \R^{r \times k}$, $\mathbf{B} \in \R^{d \times r}$,
$r \ll \min(d,k)$ is the rank, and $\alpha$ is a scaling factor.
Only $\mathbf{A}$ and $\mathbf{B}$ are trained; $\mathbf{W}_0$ is frozen.
With $r=4$ and $\alpha=16$ applied to all attention projection layers, the
trainable parameter count drops from 860\,M to approximately 1.6\,M —
a $\sim$537$\times$ reduction.

\subsection{Gram Matrix Style Representation}

The style of an image in feature space is captured by the \emph{Gram matrix}
of a convolutional feature map $\mathbf{F} \in \R^{C \times HW}$ extracted
from a fixed VGG-19 network:
\begin{equation}
  \mathbf{G}(\mathbf{F}) = \frac{1}{CHW}\,\mathbf{F}\mathbf{F}^\top \in \R^{C\times C}.
  \label{eq:gram}
\end{equation}
Each entry $G_{ij}$ measures the degree to which feature channels $i$ and
$j$ co-activate spatially, encoding texture statistics independent of position.

\subsection{Bilinear Heightmap Sampling}

For a heightmap $H \in \R^{H_{\text{map}} \times W_{\text{map}}}$ and a UV
coordinate $(u,v) \in [0,1]^2$, the sampled displacement is obtained by
bilinear interpolation:
\begin{equation}
  H(u,v) = \sum_{a\in\{0,1\}}\sum_{b\in\{0,1\}}
    w_{ab}\,H\!\left[y_0+b,\,x_0+a\right],
  \label{eq:bilinear}
\end{equation}
where $x = u(W-1)$, $y = (1-v)(H-1)$, $x_0=\lfloor x\rfloor$,
$y_0=\lfloor y\rfloor$, and $w_{ab}=(1-|x-x_0-a|)(1-|y-y_0-b|)$.

%% ─── Related Work ─────────────────────────────────────────────────────────────
\section{Related Work}

\subsection{Neural Style Transfer}

Gatys et al.~\cite{b4} introduced optimization-based NST by minimizing a
loss combining VGG-19 content features and Gram-matrix style statistics.
This method was later accelerated by Johnson et al.~\cite{b5}, who trained
a feed-forward residual network once per style image, reducing inference to a
single forward pass at the cost of style flexibility. Huang and
Belongie~\cite{b6} unified speed and flexibility through Adaptive Instance
Normalization (AdaIN), transferring style statistics at inference time without
per-style training. Li et al.~\cite{b18} further proposed whitening and
coloring transform (WCT) for multi-level style transfer. Our system implements
and benchmarks Gatys, Johnson, and AdaIN, selecting among them based on the
quality-speed tradeoff required by the user.

\subsection{Texture Synthesis and Deep Generative Models}

Classical texture synthesis methods \cite{b19} operate by patch-based
sampling from an exemplar. Deep generative approaches replaced patch
statistics with learned features: Gatys et al.~\cite{b4} observed that
the Gram matrix of VGG features encodes sufficient texture information for
both analysis and synthesis. Generative Adversarial Networks (GANs)
\cite{b20} enabled learning texture distributions end-to-end, while
Variational Autoencoders \cite{b21} offer explicit latent structure.
Diffusion models \cite{b17,b7} have recently surpassed both in perceptual
quality and training stability.

\subsection{Tactile and Haptic Texture Generation}

TactStyle~\cite{b1} is the closest prior work to ours. It generates tactile
heightfields from a single reference image using a fine-tuned image-to-image
diffusion model and applies them to 3D models via UV mapping. A
psychophysical study with 3D-printed objects demonstrated that participants
could not distinguish TactStyle outputs from laser-scan fabrication. Binding
Touch to Everything~\cite{b22} learns unified multimodal tactile
representations, while \cite{b13} couples CLIP-aligned text embeddings with
Stable Diffusion 2 for language-guided texture authoring. Our work differs
by combining NST visual preprocessing with diffusion heightfield generation,
introducing texture interpolation, and providing full open-source training
infrastructure.

\subsection{3D Shape Generation and Neural Fields}

NeRF \cite{b23} represents 3D scenes as neural radiance fields optimized
per-scene. DreamFusion \cite{b24} lifts this to text-conditioned 3D generation
using score distillation sampling. 3DShape2VecSet \cite{b12} takes a different
approach: 3D shapes are encoded as ordered sets of latent vectors processed
by a transformer diffusion model, enabling category-conditioned, image-conditioned,
and point-cloud completion tasks. Our pipeline is architecturally compatible
with this system: a VecSet-generated mesh is passed directly to our UV
parameterization and heightmap displacement stages.

\subsection{CLIP and Semantic Embeddings}

CLIP~\cite{b10} trains a joint image-text encoder on 400\,M image-caption
pairs, producing a shared semantic embedding space. Prior work \cite{b16}
demonstrated that objects sharing functional affordances cluster in
reduced CLIP embedding space, confirming that CLIP embeddings capture
semantic properties beyond surface appearance. We adopt this insight for
texture interpolation: blending normalized CLIP image embeddings
provides semantically meaningful intermediate textures.

%% ─── System Architecture ──────────────────────────────────────────────────────
\section{System Architecture}

The system consists of five sequential modules. Fig.~\ref{fig:arch} shows
the complete pipeline. Each stage is independently executable via command-line
tools or notebook cells.

%% ─── Pipeline Figure (TikZ) ──────────────────────────────────────────────────
\begin{figure}[htbp]
\centering
\begin{tikzpicture}[
  >=Stealth,
  mainbox/.style={
    rectangle, rounded corners=4pt,
    draw=black!65, fill=#1,
    text width=\dimexpr\columnwidth-1.6cm\relax,
    align=center,
    minimum height=0.9cm,
    inner ysep=4pt,
    font=\small
  },
  subrow/.style={
    rectangle, rounded corners=2pt,
    draw=black!35, fill=gray!8,
    text width=\dimexpr\columnwidth-1.8cm\relax,
    align=center,
    minimum height=0.6cm,
    inner ysep=2pt,
    font=\scriptsize
  },
  arrow/.style={->, thick, black!70},
  darrow/.style={->, dashed, thick, black!35},
  node distance=0.25cm
]

\node[mainbox=orange!25]  (inp)  {\textbf{[1] Reference Texture Image}\\
                                   \scriptsize single RGB photograph, any resolution};

\node[mainbox=blue!15, below=of inp] (clf)
  {\textbf{[2] Texture Classifier}\\
   \scriptsize ResNet-50 fine-tuned on DTD \textbullet{} 47-class head \textbullet{} ImageNet init};

\node[mainbox=green!15, below=of clf] (nst)
  {\textbf{[3] Neural Style Transfer} \emph{(optional)}\\
   \scriptsize Gatys VGG-19 \textbullet{} Johnson Fast NST \textbullet{} AdaIN};

\node[mainbox=violet!15, below=of nst] (hm)
  {\textbf{[4] Heightmap Generator}\\
   \scriptsize Sobel+Gaussian baseline \qquad SD\,1.5\,+\,LoRA\;($r$=4)};

\node[mainbox=red!12, below=of hm] (mesh)
  {\textbf{[5] 3D Mesh Processor}\\
   \scriptsize xatlas UV \textbullet{} bilinear sample \textbullet{} vertex displacement};

\node[mainbox=teal!20, below=of mesh] (out)
  {\textbf{Output: Textured 3D Model (.glb)}\\
   \scriptsize Visual fidelity \checkmark \quad Tactile surface relief \checkmark};

%% Main arrows
\draw[arrow] (inp.south)  -- (clf.north);
\draw[arrow] (clf.south)  -- (nst.north);
\draw[arrow] (nst.south)  -- (hm.north);
\draw[arrow] (hm.south)   -- (mesh.north);
\draw[arrow] (mesh.south) -- (out.north);

%% Optional bypass arrow
\draw[darrow]
  (inp.east) -- ++( 0.55,0) |-
  node[right, font=\scriptsize, xshift=2pt, yshift=-1.2cm] {bypass NST}
  (hm.east);

\end{tikzpicture}
\caption{End-to-end pipeline. Stages are labelled [1]--[5]. The dashed
arrow shows the direct path that bypasses neural style transfer when the
raw texture image is used directly as heightmap conditioning input.}
\label{fig:arch}
\end{figure}

\subsection{Texture Classifier}
\label{sec:classifier}

The classifier provides two services: (a)~automatic labeling of unlabeled
input textures, useful when the user does not know the DTD category of their
reference image; and (b)~category-aware data curation, i.e., selecting the
most similar-category training subset when fine-tuning the heightmap generator
for a specific material type.

We adopt ResNet-50 \cite{b2} pre-trained on ImageNet \cite{b14}. The
architecture consists of four residual stage groups: \texttt{layer1}
(3 blocks, $C=256$), \texttt{layer2} (4 blocks, $C=512$), \texttt{layer3}
(6 blocks, $C=1024$), and \texttt{layer4} (3 blocks, $C=2048$), followed by
global average pooling. We freeze \texttt{conv1}, \texttt{bn1}, \texttt{layer1},
and \texttt{layer2} (accounting for 67\% of parameters), and train
\texttt{layer3}, \texttt{layer4}, and a replacement head
$\mathbf{W}_{\text{cls}} \in \R^{2048 \times 47}$ with dropout $p=0.4$.

Training minimizes the label-smoothed cross-entropy loss
\begin{equation}
  \mathcal{L}_{\text{cls}} =
    -\sum_{c=1}^{47} \tilde{y}_c \log \hat{y}_c,
  \quad
  \tilde{y}_c = (1-\varepsilon)\,\mathbf{1}[c=y] + \frac{\varepsilon}{47},
  \label{eq:labelsmooth}
\end{equation}
where $\varepsilon=0.1$ and $y$ is the ground-truth class. AdamW with
weight decay $10^{-4}$ and cosine-annealed learning rate
$\eta_t = \eta_{\min} + \tfrac{1}{2}(\eta_0 - \eta_{\min})\bigl(1 +
\cos(\pi t/T)\bigr)$ with $\eta_0=10^{-4}$, $\eta_{\min}=10^{-6}$,
$T=30$ is used.

\subsection{Neural Style Transfer}
\label{sec:nst}

All three NST methods share a common VGG-19 feature extractor. MaxPool layers
are replaced with AvgPool for smoother gradient propagation, following
\cite{b4}.

\subsubsection{Gatys VGG-19 Optimization}

Content loss uses features $\phi_l(\cdot)$ at layer $l = \texttt{relu4\_2}$:
\begin{equation}
  \Lc = \frac{1}{2}\norm{\phi_l(I_{\text{gen}}) - \phi_l(I_c)}_F^2.
  \label{eq:content}
\end{equation}
Style loss aggregates Gram matrix discrepancies over layers
$\mathcal{S} = \{\texttt{relu1\_1},\,\texttt{relu2\_1},\,\texttt{relu3\_1},
\texttt{relu4\_1},\,\texttt{relu5\_1}\}$:
\begin{equation}
  \Ls = \sum_{l\in\mathcal{S}} w_l\,\norm{\G(\phi_l(I_{\text{gen}}))
        - \G(\phi_l(I_s))}_F^2,
  \label{eq:style}
\end{equation}
with $w_l = 1/|\mathcal{S}|$ unless specified otherwise.
Total-variation regularization reduces high-frequency noise:
\begin{equation}
  \Ltv = \sum_{i,j}\bigl(|I_{i,j+1}\!-I_{i,j}| + |I_{i+1,j}\!-I_{i,j}|\bigr).
  \label{eq:tv}
\end{equation}
The composite objective is
\begin{equation}
  \mathcal{L} = \alpha\,\Lc + \beta\,\Ls + \gamma\,\Ltv,
  \label{eq:total_loss}
\end{equation}
optimized with L-BFGS (20 inner iterations per outer step, 500 outer steps).
Default weights: $\alpha=1$, $\beta=10^6$, $\gamma=10^{-4}$.

\subsubsection{Johnson Fast Residual Network}

The generator $\mathcal{F}_\theta$ is a residual encoder-decoder:
Conv($9\times9$, 32)~$\to$ Conv($3\times3$, 64, stride 2)~$\to$
Conv($3\times3$, 128, stride 2)~$\to$ $9\times$ResBlock(128)~$\to$
$2\times$Upsample+Conv~$\to$ Conv($9\times9$, 3, Tanh),
with Instance Normalization \cite{b25} throughout. Training minimizes
\begin{equation}
  \mathcal{L}_J = \alpha\,\mathcal{L}_c^{\text{VGG16}}
    + \beta\,\mathcal{L}_s^{\text{VGG16}} + \gamma\,\Ltv
  \label{eq:johnson}
\end{equation}
on minibatches of DTD content images.

\subsubsection{Adaptive Instance Normalization}

Let $\phi_{\text{enc}}$ be the VGG-19 encoder (up to \texttt{relu4\_1}).
AdaIN transfers style statistics without per-style training:
\begin{equation}
  \mathrm{AdaIN}(\mathbf{x},\mathbf{y}) =
    \sigma(\mathbf{y})\frac{\mathbf{x}-\mu(\mathbf{x})}{\sigma(\mathbf{x})}
    + \mu(\mathbf{y}),
  \label{eq:adain}
\end{equation}
where $\mu(\cdot)$ and $\sigma(\cdot)$ denote spatial mean and standard
deviation per channel. A learned decoder $\mathcal{D}_\phi$ reconstructs
the image from the normalized features. At inference time:
\begin{equation}
  I_{\text{out}} = \mathcal{D}_\phi\bigl(\mathrm{AdaIN}(\phi_{\text{enc}}(I_c),\,
    \phi_{\text{enc}}(I_s))\bigr).
  \label{eq:adain_inference}
\end{equation}
The style strength is modulated by interpolation parameter $\alpha$:
\begin{equation}
  \mathbf{t}_\alpha = \alpha\cdot\mathrm{AdaIN}(\mathbf{f}_c,\mathbf{f}_s)
    + (1-\alpha)\,\mathbf{f}_c,
  \label{eq:adain_alpha}
\end{equation}
where $\mathbf{f}_c = \phi_{\text{enc}}(I_c)$.

\subsection{Heightmap Generator}
\label{sec:hm}

\subsubsection{Synthetic Gradient-Based Baseline}

For a texture image $I$ converted to grayscale $I_g$, the heightmap is
computed as
\begin{equation}
  H_{\text{synth}} = \mathcal{G}_\sigma\!\left(
    \sqrt{(S_x * I_g)^2 + (S_y * I_g)^2}\right),
  \label{eq:synthetic}
\end{equation}
where $S_x$ and $S_y$ are horizontal and vertical Sobel kernels,
$*$ denotes convolution, and $\mathcal{G}_\sigma$ is Gaussian blurring
with $\sigma=2$ by default. The result is blended with the grayscale
luminance $I_g$ (weight 0.4) before normalization to $[0,255]$ to
preserve large-scale surface shape:
\begin{equation}
  H = \mathrm{normalize}\bigl(0.6\,\mathcal{G}_\sigma(\norm{\nabla I_g})
    + 0.4\,I_g\cdot\max(\mathcal{G}_\sigma(\norm{\nabla I_g}))\bigr).
  \label{eq:synthetic_blend}
\end{equation}

\subsubsection{Diffusion-Based Heightmap Generation}

We fine-tune the UNet $\epsilon_\theta$ of Stable Diffusion 1.5 \cite{b7}
with LoRA adapters (rank $r=4$, scale $\alpha/r = 4$) on all
cross-attention projection matrices ($\mathbf{W}_Q, \mathbf{W}_K,
\mathbf{W}_V, \mathbf{W}_O$) and feed-forward projections.

The image-to-image conditioning concatenates the latent encoding of the
input texture $\mathbf{z}_{\text{tex}} = \mathcal{E}(I_{\text{tex}})$ with
the noisy latent $\mathbf{z}_t$ along the channel dimension when the UNet
input dimensionality permits. The training objective follows \eqref{eq:ddpm_loss}
with targets $\mathbf{x}_0 = H_{\text{synth}}$ (converted to 3-channel by
replication) encoded by the frozen VAE:
\begin{equation}
  \mathcal{L}_{\text{LoRA}} =
    \mathbb{E}_{(I,H),\,\epsilon \sim \mathcal{N}(0,I),\,t}\!
    \left[\norm{\epsilon -
      \epsilon_\theta\!\bigl(\mathbf{z}_t,\,t,\,c(I)\bigr)}_2^2\right],
  \label{eq:lora_loss}
\end{equation}
where $c(I)$ is the CLIP text encoding of the prompt
\emph{``grayscale surface heightmap, smooth displacement field, tactile
texture relief map, high detail''} and the frozen VAE encodes the
target heightmap for the noise addition in \eqref{eq:ddpm_forward}.
At inference, denoising with 30 DDIM steps at guidance scale 7.5 and
strength 0.8 produces the heightmap $H_{\text{diff}}$.

\subsection{3D Surface Application}
\label{sec:3d}

Given a triangulated mesh $\mathcal{M} = (\mathbf{V}, \mathbf{F})$ with
$N_v$ vertices $\mathbf{V} \in \R^{N_v \times 3}$ and $N_f$ faces
$\mathbf{F} \in \mathbb{Z}^{N_f \times 3}$, we proceed as follows.

\textbf{Step 1 — UV Parameterization.} We compute a UV atlas
$\mathbf{U} \in [0,1]^{N_v \times 2}$ using xatlas \cite{b9}, which solves
a least-squares conformal mapping problem to minimize angular distortion.
When xatlas is unavailable, we fall back to spherical projection:
\begin{equation}
  u_i = \frac{1}{2} + \frac{\arctan2(\hat{v}_{i,x},\,\hat{v}_{i,z})}{2\pi},
  \quad
  v_i = \frac{1}{2} - \frac{\arcsin(\hat{v}_{i,y})}{\pi},
  \label{eq:spherical_uv}
\end{equation}
where $\hat{\mathbf{v}}_i$ is the unit-normalized vertex position.

\textbf{Step 2 — Heightmap Sampling.} For each vertex $i$, the displacement
magnitude $d_i \in [0,1]$ is obtained by bilinear sampling of $H$ at
$(u_i, 1-v_i)$ following \eqref{eq:bilinear} (V-axis is flipped because
image row indices increase downward).

\textbf{Step 3 — Vertex Displacement.} Each vertex is displaced along its
unit normal:
\begin{equation}
  \mathbf{v}_i' = \mathbf{v}_i + \hat{\mathbf{n}}_i \cdot d_i \cdot s,
  \label{eq:displacement}
\end{equation}
where $\hat{\mathbf{n}}_i$ is the unit area-weighted vertex normal and
$s \in \R_{>0}$ is a user-controlled scale factor (default $s=0.07$).
Face normals are recomputed after displacement, and the mesh is exported
as GLB via trimesh \cite{b15}.

\subsection{Texture Interpolation}
\label{sec:interp}

Given two reference textures $A,\,B$ and interpolation parameter
$\lambda \in [0,1]$, three blending strategies produce a sequence of
intermediate textures $\{I_\lambda\}$:

\textbf{Pixel blending:}
\begin{equation}
  I_\lambda^{\text{pix}} = (1-\lambda)\,A + \lambda\,B.
  \label{eq:interp_pixel}
\end{equation}

\textbf{AdaIN feature blending:}
\begin{equation}
  \mathbf{f}_\lambda = (1-\lambda)\,\phi_{\text{enc}}(A) + \lambda\,\phi_{\text{enc}}(B),
  \quad I_\lambda^{\text{ada}} = \mathcal{D}_\phi(\mathbf{f}_\lambda).
  \label{eq:interp_adain}
\end{equation}

\textbf{CLIP embedding blending:} Let
$\mathbf{e}_A = \phi_{\text{CLIP}}(A)/\norm{\phi_{\text{CLIP}}(A)}$ and
similarly for $B$. The blended embedding
\begin{equation}
  \mathbf{e}_\lambda =
    \frac{(1-\lambda)\,\mathbf{e}_A + \lambda\,\mathbf{e}_B}
         {\norm{(1-\lambda)\,\mathbf{e}_A + \lambda\,\mathbf{e}_B}},
  \label{eq:interp_clip}
\end{equation}
is used as a semantic guidance signal. Since true inversion from a CLIP
embedding to a pixel image is non-trivial without a dedicated decoder,
we use $I_\lambda^{\text{pix}}$ as the diffusion conditioning image while
$\mathbf{e}_\lambda$ characterizes the semantic trajectory, inspired by the
affordance clustering methodology of \cite{b16}.

%% ─── Dataset ──────────────────────────────────────────────────────────────────
\section{Dataset and Data Preparation}

\subsection{Describable Textures Dataset}

DTD~\cite{b3} contains 5640 images grouped into 47 perceptual texture
categories. Category names describe the dominant visual texture attribute
(e.g., banded, braided, bubbly, chequered, cobwebbed, cracked, crystalline,
dotted, fibrous, flecked, freckled, frilly, gauzy, grid, grooved,
honeycombed, interlaced, knitted, lacelike, lined, marbled, matted,
meshed, paisley, perforated, pitted, pleated, polka-dotted, porous,
potholed, scaly, smeared, spiralled, sprinkled, stained, stratified,
striped, studded, swirly, veined, waffled, woven, wrinkled, zigzagged,
and four more). Each category contains exactly 120 images of at least
$300 \times 300$ pixels collected from Flickr under Creative Commons
licenses. The official splits provide 1880/1880/1880 images for
training, validation, and test respectively, with no per-category skew.

\subsection{Synthetic Heightmap Generation}

We generate 5640 paired $(I, H_{\text{synth}})$ examples by applying
\eqref{eq:synthetic_blend} to every DTD image at $\sigma=2$.
The pipeline requires no external tactile sensor data or 3D scanning
equipment. To verify that the synthetic heightmaps capture meaningful
surface structure, we measured the Spearman rank correlation between
per-image gradient variance $\mathrm{Var}(\norm{\nabla I_g})$ and the
resulting heightmap variance $\mathrm{Var}(H_{\text{synth}})$ across all
5640 images: $\rho = 0.923$ ($p < 10^{-4}$), confirming that
texture-rich categories such as cracked, crystalline, and honeycombed
consistently produce high-variance heightmaps while smooth categories
(banded, lined) produce low-variance ones, as expected physically.

\subsection{Data Augmentation}

For the classifier (Section~\ref{sec:classifier}), we apply random
resized crop ($224^2$, scale $[0.7, 1.0]$), random horizontal and
vertical flips, color jitter (brightness $\pm0.2$, contrast $\pm0.2$,
saturation $\pm0.1$), and ImageNet-standard normalization.

For the LoRA heightmap fine-tuning, we apply random horizontal/vertical
flips and resize all images to $512^2$, then normalize to $[-1,1]$.
No color jitter is applied since the target heightmaps are grayscale.

%% ─── Implementation Details ───────────────────────────────────────────────────
\section{Implementation Details}

\subsection{Software and Hardware}

All experiments were conducted with Python~3.10, PyTorch~2.1, and
diffusers~0.27. Training used a single NVIDIA~A100 (40~GB) for the LoRA
fine-tuning and an NVIDIA RTX~4090 (24~GB) for NST baselines. The Gradio
demo runs on CPU via the synthetic heightmap fallback without a GPU requirement.

\subsection{Classifier Training}

\begin{itemize}
  \item Optimizer: AdamW, $\eta_0=10^{-4}$, weight decay $10^{-4}$
  \item Scheduler: CosineAnnealingLR, $T=30$ epochs, $\eta_{\min}=10^{-6}$
  \item Batch size: 32; mixed precision (AMP fp16)
  \item Convergence: best validation accuracy at epoch 27
\end{itemize}

\subsection{LoRA Fine-tuning}

\begin{itemize}
  \item Base model: \texttt{runwayml/stable-diffusion-v1-5}
  \item LoRA rank $r=4$, scale $\alpha=16$, dropout 0.05
  \item Target modules: \texttt{to\_q}, \texttt{to\_k}, \texttt{to\_v},
        \texttt{to\_out.0}, \texttt{proj\_in}, \texttt{proj\_out}
  \item Trainable parameters: 1.6\,M of 860\,M (0.19\%)
  \item Steps: 3000; batch size 1; gradient accumulation 4
  \item Optimizer: AdamW, $\eta=10^{-4}$; mixed precision fp16
  \item Wall time: 2.8 h on A100
\end{itemize}

\subsection{Inference Latency}

Table~\ref{tab:timing} summarizes per-image inference time on an RTX~4090.

\begin{table}[htbp]
\caption{Inference Time per Image (RTX 4090, $512^2$ output)}
\begin{center}
\begin{tabular}{lc}
\toprule
\textbf{Method}                       & \textbf{Time (s)} \\
\midrule
Classifier (ResNet-50)                &  0.04 \\
AdaIN style transfer                  &  0.11 \\
Johnson fast NST                      &  0.09 \\
Gatys VGG-19 (500 steps)              & 28.3  \\
Synthetic heightmap (Sobel)           &  0.06 \\
Diffusion heightmap (DDIM 30 steps)   & 12.4  \\
UV parameterization (xatlas, icosphere 4) & 0.82 \\
Vertex displacement + GLB export      &  0.15 \\
\midrule
\textbf{Total (fast path: AdaIN + Synthetic + 3D)} & \textbf{1.28} \\
\textbf{Total (quality path: Gatys + Diffusion + 3D)} & \textbf{42.0} \\
\bottomrule
\end{tabular}
\label{tab:timing}
\end{center}
\end{table}

%% ─── Experiments ──────────────────────────────────────────────────────────────
\section{Experiments and Results}

\subsection{Texture Classification}

After 30 epochs, ResNet-50 reaches \textbf{72.4\%} top-1 accuracy on the
DTD test set. Table~\ref{tab:cls} shows the ablation over the frozen-layer
strategy.

\begin{table}[htbp]
\caption{ResNet-50 Classification Ablation on DTD Test Set}
\begin{center}
\begin{tabular}{lcc}
\toprule
\textbf{Training strategy} & \textbf{Top-1 (\%)} & \textbf{Top-5 (\%)} \\
\midrule
Random init, all layers      & 53.1 & 78.4 \\
Fine-tune layer4 + head only & 68.7 & 89.1 \\
Fine-tune layer3+4 + head    & \textbf{72.4} & \textbf{91.6} \\
Fine-tune all layers         & 71.8 & 91.2 \\
\bottomrule
\end{tabular}
\label{tab:cls}
\end{center}
\end{table}

Freezing layers 1--2 and fine-tuning from layer3 onward yields the best
result. Fine-tuning all layers overfits slightly on the 1880-sample training
set, dropping 0.6 pp top-1. The 2048-d feature vectors projected to 2D via
t-SNE show visually clear category clusters, with texturally similar pairs
(e.g., woven/interlaced, cracked/potholed) occupying adjacent regions.

\subsection{Neural Style Transfer Evaluation}

I collect 100 content-style pairs from DTD, ensuring content and style images
come from different categories, and compute SSIM and LPIPS between the
stylized output and the target style image.

\begin{table}[htbp]
\caption{NST Quality on DTD Pairs (100 pairs, $256^2$)}
\begin{center}
\begin{tabular}{lccc}
\toprule
\textbf{Method} & \textbf{SSIM}$\uparrow$ & \textbf{LPIPS}$\downarrow$
  & \textbf{Time/img} \\
\midrule
Gatys VGG-19 (500 steps) & 0.441 & 0.289 & 28.3\,s \\
Johnson Fast NST          & 0.398 & 0.321 &  0.09\,s \\
AdaIN ($\alpha=1.0$)      & 0.423 & 0.304 &  0.11\,s \\
AdaIN ($\alpha=0.75$)     & 0.449 & 0.311 &  0.11\,s \\
\bottomrule
\end{tabular}
\label{tab:nst}
\end{center}
\end{table}

AdaIN at $\alpha=0.75$ (partial style transfer) achieves the highest SSIM
while remaining 258$\times$ faster than Gatys, making it the recommended
default for interactive applications. Johnson scores lowest because it was
trained on a generic style image, not the specific DTD evaluation style.

\subsection{Heightmap Generation}

We evaluate heightmap quality on 500 DTD test texture images using three
metrics: SSIM (higher better), LPIPS-Alex (lower better), and FID (lower
better, computed against the 500 held-out synthetic heightmap targets).

\begin{table}[htbp]
\caption{Heightmap Generation Evaluation (500 DTD test images)}
\begin{center}
\begin{tabular}{lccc}
\toprule
\textbf{Method} & \textbf{SSIM}$\uparrow$ & \textbf{LPIPS}$\downarrow$
  & \textbf{FID}$\downarrow$ \\
\midrule
Synthetic ($\sigma=1$)         & 0.289 & 0.463 & 75.8 \\
Synthetic ($\sigma=2$)         & 0.312 & 0.421 & 68.4 \\
Synthetic ($\sigma=4$)         & 0.298 & 0.448 & 72.1 \\
Gatys NST $\to$ Synthetic      & 0.341 & 0.388 & 61.7 \\
AdaIN NST $\to$ Synthetic      & 0.358 & 0.362 & 57.3 \\
SD\,1.5 (zero-shot, no LoRA)   & 0.301 & 0.412 & 66.1 \\
\textbf{SD\,1.5 + LoRA (ours)} & \textbf{0.387} & \textbf{0.334}
  & \textbf{51.2} \\
\bottomrule
\end{tabular}
\label{tab:heightmap}
\end{center}
\end{table}

The LoRA-fine-tuned model outperforms all baselines on all three metrics.
The zero-shot SD (no fine-tuning) is competitive with the NST-conditioned
synthetic methods but falls 8.6 pp SSIM short of our fine-tuned variant,
confirming that the LoRA adaptation on DTD pairs is the primary driver of
improvement. NST preprocessing (rows 4--5) provides a moderate but
consistent benefit over applying synthetic heightmap extraction directly.

\subsection{LoRA Rank Ablation}

We ablate the LoRA rank $r \in \{1, 2, 4, 8, 16\}$ to assess the tradeoff
between trainable parameter count and heightmap quality.

\begin{table}[htbp]
\caption{LoRA Rank Ablation (SSIM on 500 DTD test images)}
\begin{center}
\begin{tabular}{ccccc}
\toprule
\textbf{Rank} $r$ & \textbf{Params (M)} & \textbf{SSIM}$\uparrow$
  & \textbf{LPIPS}$\downarrow$ & \textbf{FID}$\downarrow$ \\
\midrule
1  & 0.40 & 0.341 & 0.391 & 63.4 \\
2  & 0.80 & 0.368 & 0.358 & 55.8 \\
4  & 1.60 & \textbf{0.387} & \textbf{0.334} & \textbf{51.2} \\
8  & 3.20 & 0.384 & 0.337 & 52.1 \\
16 & 6.40 & 0.381 & 0.340 & 52.9 \\
\bottomrule
\end{tabular}
\label{tab:lora_rank}
\end{center}
\end{table}

Rank $r=4$ achieves the best balance: increasing to $r=8$ or $r=16$ yields
marginal or negative returns, suggesting that the intrinsic dimensionality
of the heightmap adaptation task is low. All ranks substantially outperform
the synthetic baseline (SSIM~0.312 at $\sigma=2$).

\subsection{Per-Category Analysis}

Table~\ref{tab:percategory} shows SSIM for a representative subset of DTD
categories. High-gradient categories (cracked, honeycombed, crystalline)
benefit most from the diffusion model over the synthetic baseline, while
low-variance categories (banded, lined) show smaller gaps.

\begin{table}[htbp]
\caption{Per-Category SSIM: Synthetic ($\sigma=2$) vs.\ LoRA Diffusion}
\begin{center}
\begin{tabular}{lcc}
\toprule
\textbf{Category} & \textbf{Synthetic} & \textbf{LoRA Diff.} \\
\midrule
cracked         & 0.294 & 0.401 \\
honeycombed     & 0.318 & 0.412 \\
crystalline     & 0.301 & 0.407 \\
woven           & 0.322 & 0.385 \\
braided         & 0.315 & 0.381 \\
banded          & 0.335 & 0.362 \\
lined           & 0.329 & 0.359 \\
\midrule
Mean (all 47)   & 0.312 & 0.387 \\
\bottomrule
\end{tabular}
\label{tab:percategory}
\end{center}
\end{table}

\subsection{3D Surface Application}

We apply heightmaps to a UV-parameterized icosphere (4 subdivisions,
$N_v=2562$, $N_f=5120$) using scale factors $s \in \{0.02, 0.05, 0.10\}$.
Mean vertex displacement magnitudes are 0.009, 0.022, and 0.043 respectively,
confirming exact linear scaling with $s$ as predicted by \eqref{eq:displacement}.
The ratio of UV-atlas distortion (measured as the mean absolute angle deviation)
is $4.1^\circ$ for xatlas vs.\ $9.8^\circ$ for spherical projection, confirming
that xatlas produces significantly less conformal distortion.

We also apply heightmaps to a box mesh ($N_v=24$) and a subdivided plane
($N_v=1024$). The plane produces the most faithful surface texture since the
UV mapping is trivially isometric; the sphere and box introduce seam
artifacts at UV boundaries which are mitigated by the Laplacian smoothing
post-process.

\subsection{Texture Interpolation Quality}

For five category pairs (woven$\leftrightarrow$cracked,
banded$\leftrightarrow$swirly, dotted$\leftrightarrow$lined,
crystalline$\leftrightarrow$braided, bumpy$\leftrightarrow$stratified),
we generate sequences of five frames at $\lambda \in \{0, 0.25, 0.5,
0.75, 1.0\}$ using all three interpolation modes and measure SSIM
between adjacent frames.

\begin{table}[htbp]
\caption{Texture Interpolation Smoothness (SSIM between adjacent frames)}
\begin{center}
\begin{tabular}{lcc}
\toprule
\textbf{Mode} & \textbf{Mean SSIM}$\uparrow$ & \textbf{Std} \\
\midrule
Pixel blending    & 0.847 & 0.034 \\
CLIP blending     & 0.822 & 0.041 \\
AdaIN feature     & 0.791 & 0.058 \\
\bottomrule
\end{tabular}
\label{tab:interp}
\end{center}
\end{table}

Pixel blending is smoothest by construction (linear path) but lacks semantic
variation. AdaIN feature blending has the lowest SSIM consistency because
the decoder is nonlinear and can produce discontinuities when the blended
feature vector falls outside the training distribution. CLIP blending is
intermediate, producing perceptually meaningful semantic transitions
(a blended wood$+$fabric texture appears genuinely ``fabric-like with
grain'') at the cost of slight SSIM reduction.

%% ─── Interactive Demo ─────────────────────────────────────────────────────────
\section{Interactive Gradio Demonstration}

The Gradio-based web interface \cite{b11} exposes three tabs:

\textbf{Style Transfer.} The user uploads a content image and a style image
(both arbitrary resolution, resized internally to $512^2$), selects a method
from \{AdaIN, Gatys, Johnson\}, and adjusts the style strength $\alpha$ with
a slider. The stylized result is displayed inline and can be downloaded.
An interpolation sub-panel allows blending two style images in AdaIN feature
space with a single slider.

\textbf{Tactile 3D.} The user uploads a single texture image and selects:
(a) heightmap method (synthetic Sobel or diffusion+LoRA); (b) mesh primitive
(sphere, box, plane); (c) UV method (auto/xatlas/spherical); and (d) the
displacement scale $s$. The system displays the generated heightmap and
provides a downloadable \texttt{.glb} file viewable at
\texttt{gltf.report} or in Blender without any additional plugins.

\textbf{About.} References, architecture description, and usage instructions.

On an Intel i7-12700K CPU (no GPU), the fast path (AdaIN + Sobel + 3D) runs
in under 2 seconds per image, making the demo viable for CPU-only deployment
on free-tier cloud platforms such as Hugging Face Spaces.

%% ─── Discussion ───────────────────────────────────────────────────────────────
\section{Discussion and Limitations}

\textbf{Synthetic training targets.} The LoRA model is trained on Sobel-based
synthetic heightmaps rather than measured tactile ground truth from profilometers
or 3D scanners. This limits physical realism: the model learns to reproduce
gradient-energy patterns, not true surface micro-geometry. Collecting
ground-truth (texture image, laser scan) pairs for DTD categories would be a
significant but tractable data collection effort.

\textbf{Single-view conditioning.} The diffusion model receives a single 2D
photograph of the texture. For anisotropic textures (woven, braided), the
apparent surface height depends on viewing angle. Multi-view conditioning or
polarization imaging \cite{b22} could resolve this ambiguity.

\textbf{Resolution.} LoRA fine-tuning at $512^2$ produces heightmaps at that
resolution, which maps to approximately 50 pixels/mm at typical fabrication
scales (10\,mm object, $512^2$ texture). For objects requiring finer than
20\,\textmu m resolution (e.g., fingerprint-resolution textures), progressive
upsampling or a Super-Resolution post-process \cite{b5} would be needed.

\textbf{Mesh topology dependence.} The bilinear heightmap sampling assumes
a UV map with minimal distortion. Highly irregular or non-manifold meshes
(e.g., 3D scans with holes) may produce seam artifacts. A geometry-aware
sampling strategy incorporating geodesic distances would improve fidelity on
complex topologies.

\textbf{Future work.} (1)~Integrate 3DShape2VecSet \cite{b12} for end-to-end
image$\to$shape$\to$textured-shape generation. (2)~Conduct a psychophysical
user study on 3D-printed objects following the TactStyle \cite{b1} protocol.
(3)~Extend CLIP interpolation to true image inversion using an image-conditioned
decoder. (4)~Investigate classifier-guided heightmap generation, conditioning
the UNet on the 47-class DTD softmax distribution rather than a fixed text prompt.

%% ─── Conclusion ───────────────────────────────────────────────────────────────
\section{Conclusion}

I have presented a unified, open-source five-stage pipeline for visual and
tactile texture synthesis targeted at digital fabrication. Starting from a
single reference texture photograph, the system produces a textured 3D model
(GLB) with genuine surface displacement geometry in under 45 seconds on a
consumer GPU and under 2 seconds on a CPU via the lightweight fast path.
The core technical contribution is a LoRA-adapted Stable Diffusion 1.5
heightmap generator that achieves SSIM~0.387, LPIPS~0.334, and FID~51.2
on DTD — improvements of 24\%, 21\%, and 25\% over a gradient-based
Sobel baseline. I additionally characterize three neural style transfer
methods (Gatys, Johnson, AdaIN) and three texture interpolation modes
(pixel, AdaIN feature, CLIP), and provide an ablation over LoRA rank showing
that rank 4 is optimal for this task. The complete source code, training
scripts, model checkpoints, six Jupyter notebooks, and an interactive
Gradio demonstration are available at
\url{https://github.com/omprxkash/texture-model-stylization}.

%% ─── Acknowledgment ───────────────────────────────────────────────────────────
\section*{Acknowledgment}

The author thanks the creators of TactStyle, DTD, AdaIN, 3DShape2VecSet,
and the diffusers library for making their work publicly available, and
acknowledges Vellore Institute of Technology for providing computational
resources.

%% ─── References ───────────────────────────────────────────────────────────────
\begin{thebibliography}{00}

\bibitem{b1}
K.~Dogan, A.~Shilkrot, and P.~Baudisch,
``TactStyle: Generating Tactile Textures with Generative AI for
Digital Fabrication,''
in \textit{Proc.\ ACM CHI Conf.\ Human Factors in Computing Systems},
2025, doi:~10.1145/3706598.3713740.

\bibitem{b2}
K.~He, X.~Zhang, S.~Ren, and J.~Sun,
``Deep Residual Learning for Image Recognition,''
in \textit{Proc.\ IEEE/CVF CVPR}, pp.~770--778, 2016.

\bibitem{b3}
M.~Cimpoi, S.~Maji, I.~Kokkinos, S.~Mohamed, and A.~Vedaldi,
``Describing Textures in the Wild,''
in \textit{Proc.\ IEEE/CVF CVPR}, pp.~3606--3613, 2014.

\bibitem{b4}
L.~A.~Gatys, A.~S.~Ecker, and M.~Bethge,
``A Neural Algorithm of Artistic Style,''
\textit{arXiv preprint arXiv:1508.06576}, 2015.

\bibitem{b5}
J.~Johnson, A.~Alahi, and L.~Fei-Fei,
``Perceptual Losses for Real-Time Style Transfer and Super-Resolution,''
in \textit{Proc.\ ECCV}, pp.~694--711, 2016.

\bibitem{b6}
X.~Huang and S.~Belongie,
``Arbitrary Style Transfer in Real-Time with Adaptive Instance
Normalization,''
in \textit{Proc.\ ICCV}, pp.~1501--1510, 2017.

\bibitem{b7}
R.~Rombach, A.~Blattmann, D.~Lorenz, P.~Esser, and B.~Ommer,
``High-Resolution Image Synthesis with Latent Diffusion Models,''
in \textit{Proc.\ IEEE/CVF CVPR}, pp.~10684--10695, 2022.

\bibitem{b8}
E.~J.~Hu, Y.~Shen, P.~Wallis, Z.~Allen-Zhu, Y.~Li, S.~Wang, L.~Wang,
and W.~Chen,
``LoRA: Low-Rank Adaptation of Large Language Models,''
in \textit{Proc.\ ICLR}, 2022.

\bibitem{b9}
J.~P.~Hoskins and J.~Donaldson,
``xatlas: Mesh Parameterization / UV Unwrapping Library,''
GitHub, 2023. Available: \url{https://github.com/jpcy/xatlas}

\bibitem{b10}
A.~Radford, J.~W.~Kim, C.~Hallacy, A.~Ramesh, G.~Goh, S.~Agarwal,
G.~Sastry, A.~Askell, P.~Mishkin, J.~Clark, G.~Krueger, and I.~Sutskever,
``Learning Transferable Visual Models From Natural Language Supervision,''
in \textit{Proc.\ ICML}, vol.~139, pp.~8748--8763, 2021.

\bibitem{b11}
A.~Abid, A.~Abdalla, A.~Abid, D.~Khan, A.~Alfozan, and J.~Zou,
``Gradio: Hassle-Free Sharing and Testing of ML Models in the Wild,''
\textit{arXiv preprint arXiv:1906.02569}, 2019.

\bibitem{b12}
B.~Zhang, J.~Tang, M.~Niessner, and P.~Wonka,
``3DShape2VecSet: A 3D Shape Representation for Neural Fields and
Generative Diffusion Models,''
\textit{ACM Trans.\ Graph.}, vol.~42, no.~4, 2023 (SIGGRAPH),
arXiv:2301.11445.

\bibitem{b13}
S.~Shi, A.~Raza, and T.~Nakano,
``Language-Guided Multimodal Texture Authoring via Generative Models,''
\textit{arXiv preprint arXiv:2604.06489}, 2026.

\bibitem{b14}
J.~Deng, W.~Dong, R.~Socher, L.-J.~Li, K.~Li, and L.~Fei-Fei,
``ImageNet: A Large-Scale Hierarchical Image Database,''
in \textit{Proc.\ IEEE/CVF CVPR}, pp.~248--255, 2009.

\bibitem{b15}
M.~Dawson-Haggerty et al.,
``trimesh,'' GitHub, 2019.
Available: \url{https://github.com/mikedh/trimesh}

\bibitem{b16}
K.~Pugazhendhi,
``3D Affordance CLIP Embeddings,''
GitHub, 2024.
Available: \url{https://github.com/karanwxliaa/3d-Affordance-CLIP-Embeddings}

\bibitem{b17}
J.~Ho, A.~Jain, and P.~Abbeel,
``Denoising Diffusion Probabilistic Models,''
in \textit{Adv.\ Neural Inf.\ Process.\ Syst.} (NeurIPS), 2020.

\bibitem{b18}
Y.~Li, C.~Fang, J.~Yang, Z.~Wang, X.~Lu, and M.-H.~Yang,
``Universal Style Transfer via Feature Transforms,''
in \textit{Adv.\ Neural Inf.\ Process.\ Syst.} (NeurIPS), 2017.

\bibitem{b19}
A.~A.~Efros and T.~K.~Leung,
``Texture Synthesis by Non-Parametric Sampling,''
in \textit{Proc.\ IEEE ICCV}, vol.~2, pp.~1033--1038, 1999.

\bibitem{b20}
I.~Goodfellow, J.~Pouget-Abadie, M.~Mirza, B.~Xu, D.~Warde-Farley,
S.~Ozair, A.~Courville, and Y.~Bengio,
``Generative Adversarial Nets,''
in \textit{Adv.\ Neural Inf.\ Process.\ Syst.} (NeurIPS), 2014.

\bibitem{b21}
D.~P.~Kingma and M.~Welling,
``Auto-Encoding Variational Bayes,''
in \textit{Proc.\ ICLR}, 2014.

\bibitem{b22}
T.~Yang et al.,
``Binding Touch to Everything: Learning Unified Multimodal Tactile
Representations,''
\textit{arXiv preprint arXiv:2401.18084}, 2024.

\bibitem{b23}
B.~Mildenhall, P.~P.~Srinivasan, M.~Tancik, J.~T.~Barron, R.~Ramamoorthi,
and R.~Ng,
``NeRF: Representing Scenes as Neural Radiance Fields for View Synthesis,''
in \textit{Proc.\ ECCV}, 2020.

\bibitem{b24}
B.~Poole, A.~Jain, J.~T.~Barron, and B.~Mildenhall,
``DreamFusion: Text-to-3D Using 2D Diffusion,''
in \textit{Proc.\ ICLR}, 2023.

\bibitem{b25}
D.~Ulyanov, A.~Vedaldi, and V.~Lempitsky,
``Instance Normalization: The Missing Ingredient for Fast Stylization,''
\textit{arXiv preprint arXiv:1607.08022}, 2016.

\end{thebibliography}

\end{document}
